SST_patterns

### 2019-08-21 SST_patterns.Rmd
update

@@

MUR_plot <- match_plot(df = MUR)

```

@@

CMC <- match_func(df = CMC_SST) %>%
  drop_na()
CMC_plot <- match_plot(df = CMC)
CMC_plot
```

@@

```{r}

```

```{r}
load("Data/site_list_sub.Rdata")
xtable(site_list_sub, auto = TRUE)
west <- site_list_sub
west$coast <- "west" # Chnages wc to west

load("Data_P1/africa_coast.RData")

@@

# Loading in the newly downloaded bathymetry data
load("Data_P1/bathy/sa_bathy.RData")

@@

# Manually correcting Sea Point and Kommetjie
site_transects$heading[5:6] <- 290 
# save(site_transects, file = "Data_P1/site_transects.RData")
load("Data_P1/site_transects.RData")

@@

# save(site_pixels, file = "Data_P1/site_pixels.RData")
load("Data_P1/site_pixels.RData")

@@

# Determining the temperature at the various distances from the coast
```

>>>>

# save(MUR, file = "Data/MUR.RData")

@@

MUR_plot <- match_plot(df = MUR)
MUR_plot
```

@@

CMC <- match_func(df = CMC_SST) %>%
  drop_na()

# save(CMC, file = "Data/CMC.RData")

CMC_plot <- match_plot(df = CMC)
CMC_plot
```

@@

```{r}
OISSTDir <- "~/Documents/Masters_2019/Data_SST"
OISST <- fread(paste0(OISSTDir, "/csvavhrr-only-v2-19810901-20180630.csv"),
            col.names = c("lon", "lat", "temp", "date"))

# Visualise the data
# To explore the data I visualise the min temperatures along the South african coastline.

OISST %>%
  filter(date == min(date)) %>%
  ggplot(aes(x = lon, y = lat)) +
  geom_raster(aes(fill = temp))

load("Data/site_list_sub.Rdata") # Loading the SACTN_overlap dataset which allows me to match it to the OISST data

unique_pixel <- OISST %>%
  select(lon, lat) %>%
  unique()

# Select nearest 1 pixels (k = 1)
# Here I use knnx to find the closes 1 pixels to the insitu sites
match_index <- knnx.index(data = as.matrix(unique_pixel[,1:2]),
                      query = as.matrix(site_list_sub[,5:6]), k = 1)

pixel_match <- unique_pixel[match_index,] %>%
  unite(col = combi, lon, lat, sep = "/", remove = F) %>%
  mutate(site = site_list_sub$site)

# Subsetting the OISST data to match the upwelling sites within the in situ collected temperature data
OISST_match <- OISST %>%
  unite(col = combi, lon, lat, sep = "/", remove = F) %>%
  filter(combi %in% pixel_match$combi)
# save(OISST_match, file = "Data/OISST_match.RData")

OISST_sites <- OISST_match %>%
  left_join(pixel_match, by = c("combi", "lon", "lat")) #%>%
  #dplyr::rename(temp_OISST =temp)

OISST_sites <- OISST_sites %>% 
  dplyr::mutate(date = as.Date(date)) %>% 
  drop_na()
# save(OISST_sites, file = "Data/OISST_sites.RData")

## Matching the Insitu data with the OISST SST data
OISST <- match_func(df = OISST_sites)
# save(OISST, file = "Data/OISST.RData")
```

Different distances from the coastline

```{r}
load("Data/site_list_sub.Rdata")
# xtable(site_list_sub, auto = TRUE)
west <- site_list_sub
west$coast <- "west" # Chnages wc to west

load("Data/africa_coast.RData")

@@

# Loading in the newly downloaded bathymetry data
load("Data/bathy/sa_bathy.RData")

@@

# Manually correcting Sea Point and Kommetjie
site_transects$heading[4:5] <- 290 
# save(site_transects, file = "Data/site_transects.RData")
load("Data/site_transects.RData")

@@

@@

# Determining the temperature at the various distances from the coast

save(site_pixels, file = "Data/site_pixels.RData")
load("Data/site_pixels.RData")
```

#
